\documentclass[a4paper]{deedy-resume-openfont}
\begin{document}
% \lastupdated
\namesection{Hiren}{Chalodiya}{
\descript{\centering Final Year (B.Tech.) | Computer Science And Engineering | IIT Jodhpur}
% \urlstyle{same}\url{} \\
\href{mailto:chalodiya.1@iitj.ac.in}{\underline{chalodiya.1@iitj.ac.in}} |  +91-8200501778}

\begin{minipage}[t]{0.36\textwidth}

\section{Education}

\subsection{IIT Jodhpur}
\descript{B.Tech in Computer Science and Engineering}
\location{Expected 2021 | Jodhpur, Rajasthan}
\location{CGPA: \bold{9.51/10} (upto 6th sem)}
\location{\bold{Department Rank: 2}}
\sectionsep

\subsection{Aashadeep Science Bhavan}
\descript{Higher Secondary Certificate}
\location{2017 | Surat, Gujarat}
\location{ Percentage : \bold{95\%} (PCM: 98.33\%)}
\sectionsep

\subsection{Sadhana Niketan Vidhyalay}
\descript{Secondary School Certificate}
\location{2015 | Surat, Gujarat}
\location{ Percentage : \bold{94.83\%}}
\sectionsep

\section{Coursework}
\subsection{Computer Science Core}
Data Structures and Algorithms \\
Object Oriented Analysis and Design \\
Algorithm Design and Analysis \\
Database Systems \\
Compiler Design \\
Operating System \\
Data Communication \\
Computer Networks \\
Software Engineering \\
Discrete Mathematics \\
Computer Organisation and Architecture \\
Theory Of Computation \\ 
Digital Logic and Design \\
Financial Engineering \\
\sectionsep

% \subsection{Mathematics}
% Probability, Statistics and Random Processes \\
% Complex Analysis and Differential Equation \\
% Linear Algebra and Calculus \\
% \sectionsep

\section{Skills}
\subsection{Programming}
\location{Proficient:}
\textbullet{} Python \textbullet{} C/C++ \\
\location{Familiar:}
\textbullet{} Java \textbullet{} JavaScript \\
% \textbullet{} TypeScript \\
\sectionsep
\subsection{Web technologies}
\textbullet{} HTML \textbullet{} CSS \\
\sectionsep
\subsection{Frameworks \& Utilities}
\textbullet{} Django \textbullet{} Solr \textbullet{} Bootstrap \\
\textbullet{} Nutch \textbullet{} Scrappy \textbullet{} React \\
\textbullet{} Electron \textbullet{} Flask \\
% \sectionsep
% \subsection{Utilities}
\textbullet{} Git \textbullet{} Jetbrains IDE \\ 
\textbullet{} Visual Studio Code
\sectionsep

\section{Links} 
\location{Github://\href{https://github.com/hirenchalodiya1}{\underline{hirenchalodiya1}}}
\location{LinkedIn://  \href{https://www.linkedin.com/in/hiren-chalodiya-277b95157/}{\underline{hiren-chalodiya-277b95157}}}
\sectionsep

\end{minipage} 
\hfill
\begin{minipage}[t]{0.63\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%             Projects            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Azure Migrate for SMB}
\descript{| Microsoft Summer Intern}
\location{May 2020 - July 2020}
\location{Mentors: Logan Smith, Damon Stephenson}
\vspace{\topsep}
\begin{tightemize}
\item Developed a prototype for cloud migration tool for SMBs
\item Designed few clicks solution for client to migrate their services to Azure within 24 hour
\item Critically analysed different approaches and implemented \textbf{lift and shift} migration approach
\item Used agent based approach to assess clients on premises machine.
\end{tightemize}

\section{Projects}
\runsubsection{AgroSearch} | 
\descript{B.Tech. Project}
\location{Jan 2019 - April 2019 | Jodhpur, India | Open sourced at  \href{https://github.com/hirenchalodiya1/agrosearch-django-server}{\underline{Github}}}
\location{Mentor: Dr. Sumit Kalra}
\begin{tightemize}
\item Developed domain based \textbf{Search engine} on Solr.
\item Built a separate \textbf{web crawler} in Python using scrappy framework.
\item Indexed \textbf{1M} sites using Nutch and customized crawler (written in python) for optimization purpose.
% \item Setup Hadoop instance for \textbf{distributed crawling}.
% \item Technologies: Solr, Nutch, Django, Scrappy % Hadoop
\end{tightemize}
\sectionsep


\runsubsection{AgriSync} | 
\descript{Software Engineering Course Project}
\location{Jan 2019 - April 2019 | Jodhpur, India } % | Open Sourced at \href{https://github.com/hirenchalodiya1/agrisync}{\underline{Github}}}
\location{Mentor: Dr. Sumit Kalra}
\begin{tightemize}
%\item Designed an \textbf{architecture} for multiple types of users.
\item Implemented the backend, designed the database and UI/UX of the platform and wrote various unit tests with \textbf{99.9\%} test \href{https://coveralls.io/github/hirenchalodiya1/agrisync}{coverage}.
\item Collaborated with three other programmers.
% \item Technologies: Django, Coverage, Coveralls, Travis
\end{tightemize}
\sectionsep

\runsubsection{Bo - the bot} | 
\descript{Microsoft Code.fun.do++ 2018}
\location{Jan 2018 - April 2018 | Jodhpur, India}
\begin{tightemize}
\item Developed a \textbf{messenger bot} to act as a helpline during natural disasters.
\item Collaborated with two other programmers.
\item Technologies: Flask, Messenger Bot Framework
\end{tightemize}
\sectionsep

\runsubsection{Gymkhana Portal} | 
\descript{Web Portal And Forum For Gymkhana}
\location{\href{https://github.com/devlup-labs/gymkhana_portal}{\underline{Project Link}} | Jodhpur, India}
\begin{tightemize}
\item Wrote various unit test cases in python with \href{https://coveralls.io/github/hirenchalodiya1/gymkhana_portal}{coverage \textbf{95\%}}.
\item Added ability to \textbf{customize HTML through admin panel}.
\item Designed UI/UX of the platform used by 1000+ users.
% \item Technologies: Django, HTML/CSS, MD Bootstrap, JavaScript
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%            Achievements         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements}
\begin{tabular}{l p{0.80\textwidth}}
2018 & Branch(CSE) \textbf{topper} of year 2017-18 at IIT Jodhpur. \\
2018 & Received Academic Excellence Award from the institute. \\
2017 & Scored \textbf{4th rank} in Gujarat state board entrance exam (ACPC). \\
2017 & JEE Advanced \textbf{AIR 2864} , JEE Mains \textbf{AIR 6037} Among Top \textbf{0.2\%} \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%             PORs                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Positions of responsibility}
\begin{tabular}{ l l l }
2018-19 & \textbf{Student Guide} & Student Counselling Service, IIT Jodhpur \\
2018-19 & \textbf{Captain} & Science Club, IIT Jodhpur \\  
\end{tabular}

\section{Extracurricular}
\begin{tabular}{ c l l }
   2018  & \textbf{Student Coordinator} & Microsoft code.fun.do++ hackathon\\
 2018-19 & \textbf{Assistant head} & IGNUS, Web-development \\
 2018-19 & \textbf{Assistant head} & IGNUS, Marketing
 \end{tabular}
 
\end{minipage} 
\end{document}